Implicit yaddayadda

### 2011-10-25 papers/PLDI2012/implicitization.tex
petites rectifs

Most SMT solvers, including Z3%
\footnote{\url{http://research.microsoft.com/en-us/um/redmond/projects/z3/}}
Yices,%
\footnote{\url{http://yices.csl.sri.com/}}
and all those supporting the full SMTLIB2 standard \cite{BarST-SMTLIB},
offer an \emph{incremental} interface: the client program specifies the formula as an initially empty conjunction, to which additional constraints are added, and calls a ``check'' function answering whether it is satisfiable; 
it may then backtrack some of the constraints and add other ones without restarting from scratch.

@@

\subsection{Path-focused technique}
\label{sec:path_focusing}

@@

Our technique gives us the expected invariant 
$\lstinline|x_old| \in~[-10000,10000]$. 
Here, only 3 paths over the 25 have been computed during the analysis. In
practice, depending on the order the SMT-solver returns the paths, other
feasible paths could have been added during the analysis.

@@

We have implemented our proposed solutions inside a prototype intraprocedural
static analyzer,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}.
We also can choose among different abstract domains: convex polyhedra, octagons,
intervals, grids (convex polyhedra and linear congruences).

For the techniques involving SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
as SMT-solver.

>>>>

Most SMT solvers, including Z3%
\footnote{\url{http://research.microsoft.com/en-us/um/redmond/projects/z3/}}
and Yices,%
\footnote{\url{http://yices.csl.sri.com/}}
and all those supporting the full SMTLIB2 standard \cite{BarST-SMTLIB},
offer an \emph{incremental} interface: the client program specifies the formula as an initially empty conjunction, to which additional constraints are added, and calls a ``check'' function answering whether it is satisfiable; 
it may then backtrack some of the constraints and add other ones without restarting from scratch.

@@

\subsection{Path-focusing}
\label{sec:path_focusing}

@@

Our technique gives us the expected invariant 
$\lstinline|x_old| \in~[-10000,\allowbreak 10000]$. 
Here, only 3 paths over the 25 have been computed during the analysis. In
practice, depending on the order the SMT-solver returns the paths, other
feasible paths could have been added during the analysis.

@@

We have implemented our proposed solutions inside a prototype intraprocedural
static analyzer,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}.
We also can choose among different abstract domains: convex polyhedra, octagons,
intervals, grids (convex polyhedra and linear congruences).
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3\cite{DBLP:conf/tacas/MouraB08}
as SMT-solver.
